---
title: "Assignment #1"
output: html_document
author: Oana Damian
---

## THE BUSINESS QUESTION
  !!!!!! please write this down well
A Brazilian food chain with more than 400 stores in Brazil has difficulties in forecasting daily of the production of specifc various food clases.

The business started with the city of São Paulo which alone responds for almost 40% of the sales(th ebusiness expects that if the process works for this city ir can be easily deployed it in the others).

We have a situation where predicting correctly how much you have to produce of each item each day is important. If the number of items produced is not  well foreasted, it can generate two types of problems:
1)	More items are produced than sold: The kind of food produced can not be stored from one day to another and therefore what is not sold has to be discharged.
2)	Less items are produced than the demand : In this scenario the company loses sales 


Today this forecast is done based on workers' experience and is far from accurate. Average loss (too much or too little) is around 10% of teh amounts produced.
Management would like to augment human decision making and would like to have a tool which would augment human decision making and cover the risk of solely depending on workers' (in their view today they relay too much in the people experience).

In addition of that they believe that the level of error is high and could be reduced.

Therefore, from the management perspective a system capable of predicting the sales would be worth having even if it doesn´t perform better than the current process. Equal performance would be acceptable. In addition of that there was an understanding that the system would be able to improve its performance overtime as more and more historical data is added to its reference database. (Machine learning effect)  



## THE DATA AVIALABLE 

## Load libraries

```{r, message = FALSE,echo = FALSE}
# Load packages
library('ggplot2') # visualization
#library('ggthemes') # visualization
library('scales') # visualization
library('dplyr') # data manipulation

#library('car')
#library('mice') # imputation
#library('randomForest') # classification algorithm

```

## Load data
```{r, message=FALSE, warning=FALSE,echo = FALSE}
DataAll <- read.csv('C:/Users/damiano/Desktop/ML_C1/Assignment1/data-06.csv', stringsAsFactors = F)
#check data str(DataAll)

```

## ANNEX1: DATA - Descriptive statistics

Each variable, explanatory and explained are analyzed w.r.t distribution and time series properties

```{r,DataAll, echo = FALSE}
#summary(DataAll[,)])
Column_Names=c("precipitac","tempmax","tempmin","tempmed","umidade","insolacao",
               "desserts","pizzas","beverage","combos","sfiha","snack","dishes","promotion","savory","salads")
Graph_Names=c("Precipitation","Maximum temperature","Minimum temperature","Medium temperature","Humidity","Unclouded",
              "Desserts","Pizza","Beverages","Combos","sfiha???","Snacks","Dishes","Promotions","Savory","Salads")
for (idx_var in 1:16)
{
par(mfrow=c(1,4))
plot(as.POSIXlt(DataAll[,c("data")],format="%m/%d/%Y"),DataAll[,c(Column_Names[idx_var])],main=Graph_Names[idx_var],xlab="",ylab="")
boxplot(DataAll[,c(Column_Names[idx_var])],main="Boxplot")
hist(DataAll[,c(Column_Names[idx_var])],main="Histogram",xlab="")
acf(DataAll[,c(Column_Names[idx_var])],main="Autocorrelation",plot = TRUE,demean = TRUE)

}

```
## ANNEX2: MODELS - The regression model
insert model results here

## ANNEX3: MODELS - The Cluster model
insert model results here

## ANNEX3: MODELS - The xxx model
insert model results here