---
title: "Asignment1_proposal2_OD"
author: "Oana Damian"
date: "9/22/2020"
output: html_document #pdf_document   #it needs LaTeX for pdf When you click the **Knit** button a html/pdf document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # echo = TRUE parameter to alow printing of the R code 
```

# Proposal 2. Forecasting Natural Gas Price using US temparatures and Natural Gas Inventories 

## Data sources

US temperature data

Description: <https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/cdus/degree_days/>

Time series : <ftp://ftp.cpc.ncep.noaa.gov/htdocs/degree_days/weighted/daily_data/2020/>


US Natural Gas Storage Dashboard

EIA Dashboard: <https://www.eia.gov/naturalgas/storage/dashboard/>

EIA Description: <https://www.eia.gov/naturalgas/storage/dashboard-content/notes_sources.pdf>





## Business case

Detect if the curent natural gas price levels are aligned with Natural Gas inventories and US temperatures


Challenges:
....


## Some graphs

```{r, echo=FALSE}
#library(quantmod)
#library(stats)
#getSymbols.FRED('FIN2140AAAMT',env=globalenv())
#getSymbols.FRED('FIN1020AAAMT',env=globalenv())
#getSymbols.FRED('FINGT80AAAMT',env=globalenv())

#plot(FIN2140AAAMT)
#plot(FIN1020AAAMT)
#plot(FINGT80AAAMT)

```


